### 2015-01-24 cav-2015-tex/motivation.tex
Updated related work, bibliography.

An ideal symbolic model should be sound, complete, and efficient. We define these terms, and their relation to existing symbolic reference models, as follows:

@@

\item[Efficient]
An efficient model of references should support analysis of sufficient complexity to represent real-world programs. Unfortunately, the only available sound and complete reference theories are too computationally inefficient to be useful for problems of practical size. For example, when dereferencing an uninitialized symbolic reference, a number of methods generate separate execution paths for each possible aliasing relationship~\cite{GSE03,KiasanKunit,Cadar:2008}. By branching at each new dereferencing operation, the number of paths created by grows exponentially with the size of the input heap.

>>>>

We posit that an ideal symbolic model should be sound, complete, and efficient. However, achieving these three goals simultaneously has proven difficult for symbolic reference analyses.

@@

\item[Efficient]
An efficient model of references should support analysis of sufficient complexity to represent real-world programs. Unfortunately, many reference theories are too computationally inefficient to be useful for problems of practical size. For example, when dereferencing an uninitialized symbolic reference, a number of methods generate separate execution paths for each possible aliasing relationship~\cite{GSE03,KiasanKunit,Cadar:2008}. By branching at each new dereferencing operation, the number of paths created by grows exponentially with the size of the input heap.

### 2015-01-24 cav-2015-tex/rw.tex
Updated related work, bibliography.

\noindent\textbf{Symbolic Execution} 
Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive primitive
types~\cite{Clarke:76,King:76}. Several recent projects generalized
the core idea of symbolic execution which enabled it to be applied to
programs with more general types, including references and
arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during
symbolic execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths than
GSE techniques.

Key limitations of symbolic execution include path explosion and non-symbolic operations. Mitigation of the path explosion problem has focused on composition, modular analysis, and state merging. Dynamic Symbolic Execution is the primary technique to circumvent the limitations of constraint solvers.

More recently, dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically. ~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously. When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues. When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path. Initial DSE attempts

In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them. A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis. The SAGE DSE engine includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}. However, SAGE only accepts programs where memory allocation is independent of the of program inputs, and as such does not support a complete theory of computation.

\noindent\textbf{Bounded Model Checking}

@@

\noindent\textbf{Test Input Generation}

\noindent\textbf{Symbolic Value Sets}
A number of techniques use value sets. Some of them are general techniques where all program values are represented using value sets. While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished. Others use value sets specifically in the context of referencing operations, however, these methods suffer from other limitations.

>>>>

\noindent\textbf{Symbolic Execution} 
Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive primitive
types~\cite{Clarke:76,King:76}. Limitations of early symbolic execution techniques includes non-primitive data types, path explosion and non-symbolic operations. Subsequent adaptations of symbolic execution have sought to overcome these limitations.

To address the issue of references, several projects have generalized
the core idea of symbolic execution, enabling it to be applied to
programs with more general types, including references and
arrays~\cite{GSE03,KiasanKunit,Rosner:2015}. However, these generalized symbolic execution (GSE) techniques universally require nondeterministic case-splitting during dereferencing operations, thus exacerbating the path explosion problem. Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during
symbolic execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths than
GSE techniques.

Recent progress has been made towards mitigating path explosion via state merging~\cite{Kuznetsov:2012,Sen:2014,Torlak:2014}. While the independently developed techniques in~\cite{Sen:2014,Torlak:2014} use representations similar to the one presented here, none of these techniques address the fundamental issue concerning symbolic heaps, namely dereferencing symbolic input references. For these reasons, we believe these works to be both orthogonal and complimentary to our own.

Dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically. ~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously. When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues. When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path. While concretization allows DSE to explore a much wider selection of programs, this freedom comes at the price of completeness. The process of concretization introduces approximation such that

In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them. A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis. The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}. However, the heap model in SAGE requires fixing the size of the memory prior to starting the analysis, and is therefore not complete.

\noindent\textbf{Bounded Model Checking}
Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition. The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis. Many BMC methods include a model for reasoning about references, including those described in ~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis. By extension, the reference models used in BMC methods are generally not complete. Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.

@@

\noindent\textbf{Symbolic Heap Representations}
% a good place to mention procedure summaries, like Yorsh and the Dilligs.
Our work builds upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references. While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing. All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} do not perform a complete analysis.
